\section{Relevant Research and Publications}



\orderedouterlist{




\entrybig
{\textbf{Bayesian Search for IMBHs in LIGO data}}
{Published in MNRAS}
{Implemented and ran a Bayesian search for IMBH in O2 data.}
{\link{https://arxiv.org/abs/2107.12109}{arXiv:2107.12109}}
\innerlist{
	\entrylabeled[--]{Ran $\sim0.2$M Bayesian PE analyses, totaling 1.2M core-hours.}
	\entrylabeled[--]{In addition to finding previously detected GW events, we discovered a few new GW candidates.}
	\entrylabeled[--]{\gitligo{avi.vajpeyi/bcr\_pipeline}}
}

\entrybig
{\textbf{Measuring properties of AGN disks with gravitational waves}}
{Published in ApJ}
{Constructed a stellar mass BH population model for BH merging in AGN disks.}
{\link{https://arxiv.org/abs/2111.03992}{arXiv:2111.03992}}
\innerlist{
	\entrylabeled[--]{Simulated two AGN black hole populations.}
	\entrylabeled[--]{Demonstrated O(200) events required before AGN parameters can be measured.}
	\entrylabeled[--]{\github{avivajpeyi/agn\_phenomenological\_model}}
}


\entrybig
{\textbf{Bayesian Parameter Estimation Deep-followup for GW Events}}
{Under review, ApJ}
{Devising and utilising a ``deep-followup'' Bayesian analysis method on GW candidates.}
{\link{https://arxiv.org/abs/2203.13406}{arXiv:2203.13406}}
\innerlist{
    \entrylabeled[--]{Demonstrate the mathematical path to constrain a few dependent priors.}
    \entrylabeled[--]{Analysing GW events with ambiguous PE results.}
    \entrylabeled[--]{\github{avivajpeyi/deep\_gw\_pe\_followup}}
}

\entrybig
{\textbf{TESS-Atlas}}
{In prep}
{Obtaining Bayesian PE fits and cataloging all TESS Objects of interest with a transit model.}
{\link{https://github.com/dfm/tess-atlas}{dfm/tess-atlas}}
\innerlist{
	\entrylabeled[--]{First Bayesian PE catalog for all TESS objects of interest.}
	\entrylabeled[--]{Fitting for systems with data for multiple-transits, single-transits, and multiple-planets.}
	\entrylabeled[--]{\github{dfm/tess-atlas}}
}

\entrybig
{\textbf{Postdoctoral Research Fellow}}
{University of Auckland, 2023--present}
{Developing Bayesian noise-modeling and evidence-estimation methods for LISA and LVK gravitational-wave data analysis, supervised by Prof. Renate Meyer.}
{\link{https://scholar.google.com/citations?user=hP-8RuUAAAAJ}{Google Scholar}}
\innerlist{
	\entrylabeled[--]{\link{https://arxiv.org/abs/2510.00533}{Bayesian power spectral density estimation for LISA noise based on P-splines with a parametric boost}}
	\entrylabeled[--]{\link{https://arxiv.org/abs/2512.10283}{MorphZ: Enhancing evidence estimation through the Morph approximation}}
}

}


\vspace*{10pt}
A full list of short-author paper that I have contributed to can be found \textcolor{color-title}{\hyperref[publications]{here}}.

