
\section{Teaching}


\textbf{Monash University: Teaching Assistant}
\denseouterlist{



\entrymid[\textbullet]
{[FIT:3170] Software engineering practice}
{Feb-Nov `21}
{Mentored two teams of 15 students to develop applications for a client using ``Lean sAFE''.}

\entrymid[\textbullet]
{[FIT:9136] Algorithms and foundations}
{Mar-June `20}
{Ran online python workshops, helped create assignments and an automated-grading system.}

\entrymid[\textbullet]
{[FIT:1048] Fundamentals of C++}{July-Nov `19}
{Conducted tutorials to help give students practical experience with C++ programming.}

}

\textbf{Independent Tutoring}

\denseouterlist{

\entrymid[\textbullet]
{AP Physics and Calculus}
{Oct-Dec `18}
{Tutored 2 advanced-placement high school students on physics and calculus.}

}


\textbf{The College of Wooster: Teaching Assistant}
\denseouterlist{

\entrymid[\textbullet]
{[PHYS:201] Modern Physics Lab}
{Feb-June `18}
{Helped students with lab experiments, scientific writing, and presentation of data. 
Some expts: Millikan Oil-drop, Photoelectric Effect and Rutherford Scattering.}
    
\entrymid[\textbullet]
{[PHYS:112] Calculus Physics 2 Lab}
{Aug-Dec `17}
{Help introductory physics students with lab experiments and data analysis.}
    
\entrymid[\textbullet]
{[IDPT:405] Entrepreneurship}
{Aug-Dec `16}
{Facilitate activities to engage students in the ``Social Change Model of Leadership Development''.}
  
\entrymid[\textbullet]
{[CS:200] Algo. Analysis}
{Aug-Dec `16} 
{Intro to computation complexity theory, Big-O notation, and algorithms (dynamic, greedy, etc.)}
    
\entrymid[\textbullet]
{[CS:120] Data Structures and Algos.}
{Feb-June `16}
{Run labs focused on C++ OOP, testing and documentation.}
    
\entrymid[\textbullet]
{[IDPT:1991] Global Engagement}
{Aug-Dec `15}
{Stimulate class discussions on social and cultural topics and helped with class management.}


}




